Introducing statistics with \\texttt{intRo}

### 2014-12-04 student-paper-competition-2014/paper.Rmd
Blurb about printing

Once students get pulled in by an easy to use interface and fun interaction with their data, \texttt{intRo} has an ulterior motive: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well.

>>>>

Once students get pulled in by an easy to use interface and fun interaction with their data, \texttt{intRo} has an ulterior motive: to get students excited about programming. By navigating about the user interface of \texttt{intRo}, students are actually creating a fully-executable \texttt{R} script that they can download and run locally as well as viewing the script change real-time within the application. This code creation element of \texttt{intRo} is meant to generate excitement about programming in \texttt{R} and empower students to feel that they can generate code as well. \texttt{intRo} uses \texttt{rmarkdown}'s [@rmarkdown] \texttt{render} function in order to print the results, by dymanically executing the user's \texttt{R} script. By default, the output will include the \texttt{R} code, but if the user elects to hide the source code by clicking the code toggle button at the top, the code will not appear in the printed results.
